A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus \\ (Draft)

### 2014-08-06 Papers/NaturalDeduction/GodProof-ND.tex
Improve ND paper

\documentclass{article}

\usepackage{fancybox}
\usepackage{latexsym}
\usepackage{proof}
\usepackage{bussproofs}
\EnableBpAbbreviations
\newcommand{\rl}[1]{\RightLabel{#1}}

@@

@@

\begin{calculus}
{The intuitionistic natural deduction calculus \ND}
{fig:ND}

@@

\s\s
\infer[\imp_I]{A \imp B}{ B }
\s\s
\infer[\imp_I^n]{A \imp B}{ \infer*{B}{\infer[n]{A}{}} }
\s\s
\infer[\imp_E]{B}{A & A \imp B}

@@

@@

We let negation be a defined concept by $\neg A\equiv A\imp \bot$. The rules for negation introduction and elimination are special cases of the implication rules. Equivalence is also a defined concept with  $ (A\biimp B)\equiv (A\imp B)\wedge (B\imp A)$. 
\end{calculus}

\begin{calculus}
{Classical Rule: Double negation elimination}
{fig:Classical}
\infer[\neg\neg_E]{A}{ \neg\neg A }
\end{calculus}

@@

\s\s\s\s
\infer[\nec_I]{\nec A}{\eta: \fbox{\infer*{A}{}} }
\s\s\s\s\s
\infer[\nec_E]{n: \fbox{ \infer*{}{A} } }{\nec A}

\s\s\s\s
\infer[\pos_I]{\pos A}{n: \fbox{\infer*{A}{}} }
\s\s\s\s\s
\infer[\pos_E]{\eta: \fbox{ \infer*{}{A} } }{\pos A}

@@

\noindent
A \emph{derivation} is a directed acyclich graph whose nodes are formulas and whose edges correspond to applications of the inference rules shown in Figures \ref{fig:ND} and \ref{fig:NDK}. Parts of a derivation may be surrounded by boxes. A \emph{proof} is a derivation that additionally satisfies the following conditions:

\begin{itemize}
\item \textbf{eigen-variable conditions:}
if $\rho$ is a $\all_I$ inference eliminating a variable $\alpha$, then any occurrence of $\alpha$ in the proof should be an ancestor of the occurrence of $\alpha$ eliminated by $\rho$;
if $\rho$ is a $\ex_E$ inference introducing a variable $\beta$, then any occurrence of $\beta$ in the proof should be a descendant of the occurrence of $\beta$ introduced by $\rho$.
%
\item \textbf{eigen-box conditions:} $\eta$ must be a fresh name for a box.
%
\item \textbf{boxed assumption condition:} any assumption should be discharged within the box where it is made.
%
\item \textbf{unboxed root condition:} the proof's root should not be inside any box.
\end{itemize}

@@

\section{Scott's Proof}

@@

@@

@@

\section{Proof system equivalent to system K}

>>>>

\documentclass{llncs}

\usepackage{fancybox}
\usepackage{latexsym}
\usepackage{proof}
\usepackage{bussproofs}
\usepackage{amsmath}
\EnableBpAbbreviations
\newcommand{\rl}[1]{\RightLabel{#1}}

@@

The language of higher-order modal logic used here is inspired by that of Church's simple type theory \citep{church}.

\begin{definition} \emph{Simple types} are given by the following grammar:
$$
  \theta,\tau \quad ::= \quad \mu \ \mid \ o \ \mid \ \theta \imp \tau
$$
where $\mu$ is the atomic type for individuals, $o$ is the atomic type for propositions and $\theta \imp \tau$ is the type for functions taking an argument of type $\theta$ and returning something of type $\tau$. `$\imp$' is assumed to be right associative.
\end{definition}

\begin{definition} \emph{Terms and formulas} are given by the following grammar:
\begin{align*}
 s,t \quad ::= \quad & 
  p_\tau \ \mid \ 
  X_\tau \ \mid \
  (\lambda X_\theta.s_\tau)_{\theta\imp\tau} \ \mid \ 
  (s_{\theta\imp\tau}\, t_\theta)_\tau \ \mid \\
& \bot_o \ \mid \
  \imp_{o\imp o\imp o} \ \mid \ 
  \wedge_{o\imp o\imp o} \ \mid \
  \vee_{o\imp o\imp o} \ \mid \\
& \all_{(\tau\imp o)\imp o} \ \mid \ 
  \ex_{(\tau\imp o)\imp o} \ \mid \
  \nec_{o\imp o} \ \mid \
  \pos_{o\imp o}
\end{align*}
where $p_\tau$ and $X_\tau$ range over, respectively, constants and variables of type $\tau$. Parenthesis conventions, infix notation for propositional connectives and binding notation for quantifiers are assumed. Furthermore, subscript types are omitted when they are clear from the context. Negation ($\neg_{o\imp o}$) and equivalence ($\biimp_{o\imp o\imp o}$) are defined by $\neg A\equiv A\imp \bot$ and $ (A\biimp B)\equiv (A\imp B)\wedge (B\imp A)$.
\end{definition}

For Natural deduction

beta reduction

@@

\begin{calculus}
{propositional rules}
{fig:ND}

@@

\s\s
\infer[\bot_E]{A}{ \bot }
\s
\infer[\imp_I]{A \imp B}{ B }
\s
\infer[\imp_I^n]{A \imp B}{ \infer*{B}{\infer[n]{A}{}} }
\s
\infer[\imp_E]{B}{A & A \imp B}

@@

\begin{calculus}
{double negation elimination}
{fig:Classical}
\infer[\neg\neg_E]{A}{ \neg\neg A }
\end{calculus}

\begin{calculus}
{quantifier rules}
{fig:QuantifierRules}

@@

\end{calculus}

@@

\s\s\s\s
\infer[\nec_I]{\nec A}{\omega: \fbox{\infer*{A}{}} }
\s\s\s\s
\infer[\nec_E]{w: \fbox{ \infer*{}{A} } }{\nec A}

% \vspace{2em}

% \s\s\s\s
% \infer[\pos_I]{\pos A}{n: \fbox{\infer*{A}{}} }
% \s\s\s\s\s
% \infer[\pos_E]{\eta: \fbox{ \infer*{}{A} } }{\pos A}

@@

\noindent
A \emph{derivation} is a directed acyclic graph whose nodes are formulas and whose edges correspond to applications of the inference rules shown in Figures \ref{fig:ND}, \ref{fig:Classical} and \ref{fig:NDK}. Parts of a derivation may be surrounded by boxes. A \emph{proof} is a derivation that additionally satisfies the following conditions:

\begin{itemize}
\item \textbf{eigen-variable conditions:}
if $\rho$ is a $\all_I$ inference eliminating a variable $\alpha$, then any occurrence of $\alpha$ in the proof should be an ancestor of the occurrence of $\alpha$ eliminated by $\rho$;
if $\rho$ is a $\ex_E$ inference introducing a variable $\beta$, then any occurrence of $\beta$ in the proof should be a descendant of the occurrence of $\beta$ introduced by $\rho$.
%
\item \textbf{eigen-box conditions:} $\omega$ must be a fresh name for a box.
%
\item \textbf{boxed assumption condition:} any assumption should be discharged within the box where it is made.
%
\item \textbf{unboxed root condition:} the proof's root should not be inside any box.
\end{itemize}

@@

\subsection{Suitability for K}

\section{Scott's Proof in Natural Deduction}

@@

\section{New Proof}

@@

\setcounter{axiom}{0}

@@
